Manuscript Figures

### 2024-05-30 Manuscript_Figures.Rmd
Create example LANDIS mapcodes, fix mapcode mismach

Read in IC map and IC csv. Find tree species with highest biomass for each MapCode, then add that info to the raster.
```{r}
IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
IC_file <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
IC_dom <- IC_file %>%
  group_by(MapCode,SpeciesName) %>%
  summarize(total_sp_biomass = sum(CohortBiomass)) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  slice_max(total_sp_biomass) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "Oak spp.",
                                 SpeciesName=="TurkeyOak" ~ "Oak spp.",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Longleaf Pine",
                                "Loblolly Pine",
                                "Slash Pine",
                                "Shortleaf Pine",
                                "Tulip Poplar",
                                "Sweetgum",
                                "Red Maple",
                                "Oak spp."
                              ))) %>%
  mutate(SpeciesID = as.numeric(SpeciesName))
IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_map_dom <- left_join(IC_map_df, IC_dom)
IC_map_rst <- IC_map_dom %>% select(SpeciesID)
mapcodes <- unique(IC_map_dom$SpeciesID)
sp_names <- unique(IC_map_dom$SpeciesName)
IC_levels <- tibble("id"=mapcodes, "levels"=sp_names) %>% drop_na()
IC_map$IC_map_rst <- IC_map_rst
IC_dom_map <- IC_map$IC_map_rst
levels(IC_dom_map) <- IC_levels
```

```{r}
ggplot() +
  geom_spatraster(data=IC_dom_map) +
  scale_fill_colorblind() +
  labs(fill="Dominant Tree Species") +
  theme_bw()
#TODO: Reorder legend, remove NA
```

@@

IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_df <- BA_split %>% select(MapCode,IC_ID)
F2D_df <- BA_split %>% select(MapCode,F2D_ID)
F2W_df <- BA_split %>% select(MapCode,F2W_ID)
F5D_df <- BA_split %>% select(MapCode,F5D_ID)
F5W_df <- BA_split %>% select(MapCode,F5W_ID)

@@

@@

```{r}
treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","Treelist_postlandis_cycle0.csv"))
set.seed = 14
sample_mapcode <- sample(unique(treelist$MapCode),1)
mapcode <- treelist %>% filter(MapCode == sample_mapcode)
mapcodes <- treelist %>%
  filter((X>=100 & X<=300) & (Y>=500 & Y<=700))

@@

tree_polys <- list()
for(i in 1:nrow(mapcodes_vect)){
  tree_i <- mapcodes_vect[i,]
  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
  tree_polys[[i]] <- buffer_i
}
mapcodes_poly <- vect(tree_polys)
writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
mapcodes_poly <- arrange(mapcodes_poly, CD_m)

example_mapcode <- ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_spatvector(data=mapcodes_poly, aes(fill=SPECIES_SYMBOL, color=SPECIES_SYMBOL), alpha=0.7) +
  scale_fill_colorblind() +
  scale_color_colorblind() +
  labs(x = "X (m)",
       y = "Y (m)",
       fill = "Species",
       color="Species") +
  theme_bw()
example_mapcode
ggsave("example_mapcode.jpg",path = here("Plots"))

@@

>>>>

Read in IC map and IC csv. Find tree species with highest biomass for each MapCode, then add that info to the raster.
```{r}
IC_tif <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","output-community-0.img"))
crs(IC_map) <- crs(IC_tif)
ext(IC_map) <- ext(IC_tif)

FB_shp <- vect(here("FtBraggBoundary","FtBraggBoundary.shp"))
FB_shp <- project(FB_shp, IC_map)
FB_shp <- crop(FB_shp, IC_map)

IC_file <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
IC_dom <- IC_file %>%
  group_by(MapCode,SpeciesName) %>%
  summarize(total_sp_biomass = sum(CohortBiomass)) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  slice_max(total_sp_biomass) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "Oak spp.",
                                 SpeciesName=="TurkeyOak" ~ "Oak spp.",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Oak spp.",
                                "Sweetgum",
                                "Red Maple",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Shortleaf Pine",
                                "Tulip Poplar"
                              ))) %>%
  mutate(SpeciesID = as.numeric(SpeciesName))
IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = Layer_1)
IC_map_dom <- left_join(IC_map_df, IC_dom) %>%
  mutate(SpeciesName = case_when(is.na(SpeciesName) ~ "Non-Forest",
                                 TRUE ~ SpeciesName)) %>%
  mutate(SpeciesID = case_when(SpeciesName=="Non-Forest" ~ 9,
                               TRUE ~ SpeciesID))

sp_names <- c(
  "Oak spp.",
  "Sweetgum",
  "Red Maple",
  "Slash Pine",
  "Loblolly Pine",
  "Longleaf Pine",
  "Shortleaf Pine",
  "Tulip Poplar",
  "Non-Forest"
)

IC_map_rst <- IC_map_dom %>% select(SpeciesID)
IC_map$IC_map_rst <- IC_map_rst
IC_dom_map <- IC_map$IC_map_rst
IC_dom_map <- IC_dom_map %>% mutate(IC_map_rst = factor(IC_map_rst, labels = sp_names))
IC_dom_map <- mask(IC_dom_map, FB_shp)
```

```{r}
bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
  project(crs(IC_dom_map))
map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
ggplot() +
  geom_spatraster(data=IC_dom_map) +
  geom_spatvector(data=bp4, fill=NA, color = "red", linewidth = 0.75) +
  scale_fill_manual(values=map_colors, na.value = NA) +
  labs(fill="Dominant Tree Species") +
  theme_bw()
ggsave("IC_map.jpg", path=here("Plots"), width = 7, height = 3)
```

@@

IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = Layer_1)
IC_df <- BA_split %>% select(MapCode,IC_ID)
F2D_df <- BA_split %>% select(MapCode,F2D_ID)
F2W_df <- BA_split %>% select(MapCode,F2W_ID)
F5D_df <- BA_split %>% select(MapCode,F5D_ID)
F5W_df <- BA_split %>% select(MapCode,F5W_ID)

@@

### Stacked bar chart of species composition in burn plot
```{r}
bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
BA_plot <- before_after %>% 
  filter(MapCode %in% bp_mapcodes) %>%
  group_by(pre_post, SpeciesName) %>%
  summarize(CohortAge_Avg = mean(CohortAge),
            CohortBiomass_Sum = sum(CohortBiomass)) %>%
  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
                                                "Fire2-Dry",
                                                "Fire2-Wet",
                                                "Fire5-Dry",
                                                "Fire5-Wet"))) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "White Oak",
                                "Turkey Oak",
                                "Sweetgum",
                                "Red Maple",
                                "Shortleaf Pine",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Tulip Poplar"
                              )))

bar_colors <- colorblind_pal()(8)[c(2,3,1,4,5,6,8)]
stacked_barchart <- BA_plot %>%
  ggplot() +
  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
  scale_fill_manual(values=bar_colors) +
  labs(x="LANDIS Run",
       y="Total Biomass (kg)",
       fill="Species") +
  theme_bw()
stacked_barchart

ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
```

@@

```{r}
treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","Treelist_postlandis_cycle0.csv"))
mapcodes <- treelist %>%
  filter((X>=100 & X<=300) & (Y>=500 & Y<=700))

@@

tree_polys <- list()
for(i in 1:nrow(mapcodes_vect)){
  tree_i <- mapcodes_vect[i,]
  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
  tree_polys[[i]] <- buffer_i
}
mapcodes_poly <- vect(tree_polys)
writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"), overwrite=T)
mapcodes_poly <- mapcodes_poly %>%
  arrange(CD_m) %>%
  mutate(SpeciesName = case_when(SPECIES_SYMBOL=="PITA" ~ "Loblolly Pine",
                                 SPECIES_SYMBOL=="PIPA2" ~ "Longleaf Pine",
                                 SPECIES_SYMBOL=="PIEL" ~ "Slash Pine",
                                 SPECIES_SYMBOL=="LIST2" ~ "Tulip Poplar", #I know this is actually sweetgum
                                 SPECIES_SYMBOL=="ACRU" ~ "Red Maple",
                                 TRUE ~ "Other")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Other",
                                "Red Maple",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Tulip Poplar"
                              )))

new_colors <- colorblind_pal()(8)[c(1,4,5,6,8)]
example_mapcode <- ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_hline(yintercept = 700, linetype = "dashed") +
  geom_vline(xintercept = 100, linetype = "dashed") +
  geom_hline(yintercept = 500, linetype = "dashed") +
  geom_vline(xintercept = 300, linetype = "dashed") +
  geom_spatvector(data=mapcodes_poly, aes(fill=SpeciesName, color=SpeciesName), alpha=0.7) +
  scale_fill_manual(values = new_colors) +
  scale_color_manual(values = new_colors) +
  labs(x = "X (m)",
       y = "Y (m)",
       fill = "Species",
       color="Species") +
  theme_bw()
example_mapcode
ggsave("example_mapcode.jpg",path = here("Plots"), height=6)

empty_mapcode <- ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_hline(yintercept = 700, linetype = "dashed") +
  geom_vline(xintercept = 100, linetype = "dashed") +
  geom_hline(yintercept = 500, linetype = "dashed") +
  geom_vline(xintercept = 300, linetype = "dashed") +
  geom_spatvector(data=mapcodes_poly, fill=NA, color=NA) +
  labs(x = "X (m)",
       y = "Y (m)") +
  theme_bw()
empty_mapcode
ggsave("empty_mapcode.jpg",path = here("Plots"), height=6)

@@

```{r}
example_mapcodes <- unique(mapcodes$MapCode)
community50 <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-50.csv"))
landis_examples <- community50 %>% filter(MapCode %in% example_mapcodes)
View(landis_examples)

ex_colors1 <- colorblind_pal()(8)[c(5,6)]
ex_colors2 <- colorblind_pal()(8)[c(5,6,8)]
ex_colors3 <- colorblind_pal()(8)[c(1,4,5)]
ex_colors4 <- colorblind_pal()(8)[c(1,4,5)]
ex_colors <- list(ex_colors4,ex_colors2,ex_colors3,ex_colors1)
for(i in 1:length(example_mapcodes)){
  landis_examples %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SweetGum" ~ "Tulip Poplar",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="RedMaple" ~ "Red Maple")) %>%
  mutate(SpeciesName = factor(SpeciesName, 
                              levels = c("Red Maple",
                                         "Slash Pine",
                                         "Loblolly Pine",
                                         "Longleaf Pine",
                                         "Tulip Poplar")),
         CohortAge = factor(CohortAge)) %>%
  filter(MapCode == example_mapcodes[i]) %>%
  ggplot() +
    geom_bar(stat="identity", 
             position=position_dodge2(preserve = "single", padding = 0.2), 
             aes(x=interaction(CohortAge,SpeciesName,sep="-"),
                 y=CohortBiomass,
                 fill=SpeciesName)) +
    scale_x_discrete(labels = function(x) gsub("-.*","", x),limits=rev) +
    scale_fill_manual(values = ex_colors[[i]]) +
    scale_y_continuous(limits = c(0,3800)) +
    labs(x="Cohort Age",y="Cohort Biomass") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "none",
          # axis.title = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank())
  ggsave(paste0("ex_biomass_",example_mapcodes[i],".jpg"), path=here("Plots"), height=2, width=2.15)
}
```
